Insert your title here

### 2023-07-26 manuscript_JQAS/manuscript_JQAS.tex
updating writings, citations, and coding

\usepackage[utf8]{inputenc}				%(only for the pdftex engine)
%\RequirePackage[no-math]{fontspec}[2017/03/31]%(only for the luatex or the xetex engine)
\usepackage[big,online]{dgruyter}	%values: small,big | online,print,work
\usepackage{lmodern} 
\usepackage{microtype}
\usepackage[numbers,square,sort&compress]{natbib}

@@

\begin{document}

@@

\author*[1]{Mena Q.Whalen}
%\ use * to mark the author as the corresponding author
\author[2]{Brian Mills}
\author[3]{Gregory J. Matthews} 
\runningauthor{Whalen et al.}
\affil[1]{\protect\raggedright 
Loyola University Chicago, Department of Mathematics and Statistics, Chicago, IL, USA, e-mail: mwhalen@luc.edu}
\affil[2]{\protect\raggedright 
University of Texas at Austin, Department of Kinesiology and Health Education, Austin, TX, USA, e-mail: brian.mills@austin.utexas.edu}
\affil[3]{\protect\raggedright 
Loyola University Chicago, Department of Mathematics and Statistics, Chicago, IL, USA, e-mail: gmatthews1@luc.edu}

@@

<<echo = FALSE, message = FALSE, warning = FALSE>>=
library(tidyverse)
library(janitor)
library(hdbinseg)

teams <- read_csv("/Users/gregorymatthews/Dropbox/baseball_cpt/data/Teams.csv") %>% 
  clean_names()

team_names <- teams %>% 
  group_by(franch_id) %>% 
  count() %>% 
  filter(n > 120) %>% 
  pull(franch_id)

# teams %>% 
#   filter(franch_id %in% team_names) %>% 
#   group_by(franch_id) %>% 
#   summarise(min(year_id)) ## filter after 1901

old_teams_full <- teams %>% 
  filter(franch_id %in% team_names & year_id > 1900) %>% 
  select(year_id, franch_id, w, l, r, ab, h, hr, bb, so)

teams_wide <- old_teams_full %>% 
  pivot_wider(id_cols = franch_id, 
              names_from = year_id, 
              values_from = hr)

## find thresholding value for cpt using bootstrapping
thrs <- dcbs.thr(as.matrix(teams_wide[-1]), interval = c(1, dim(teams_wide[-1])[2]))
### if I lower the threshold more changepoints
hr_cpt_dcbs <- dcbs.alg(as.matrix(teams_wide[-1]), cp.type = 1, thr = thrs-1)
hr_cpt_dcbs$ecp
hr_cpt_sbs <- sbs.alg(as.matrix(teams_wide[-1]), cp.type = 1)         
hr_cpt_sbs$ecp

cpt_years <- as.numeric(names(teams_wide[-1])[hr_cpt_dcbs$ecp])

ggplot(old_teams_full, aes(year_id, hr, color = franch_id)) +
  geom_line() +
  geom_vline(xintercept = cpt_years)

@

%
% # <<>>=
% # load("./baseball_cpt/data/teams_cpt_time_df.RData")
% # teams_cpt_time_df
% # @
%

>>>>

\usepackage[utf8]{inputenc}				%(only for the pdftex engine)
%\RequirePackage[no-math]{fontspec}[2017/03/31]%(only for the luatex or the xetex engine)

\usepackage{lmodern} 
\usepackage{microtype}
\usepackage[numbers,square,sort&compress]{natbib}
\usepackage[big,online]{dgruyter}	%values: small,big | online,print,work

@@

\usepackage{Sweave}
\begin{document}
\input{manuscript_JQAS-concordance}

@@

\author*[1]{Mena C.R. Whalen}
%\ use * to mark the author as the corresponding author
\author[2]{Brian Mills}
\author[3]{Gregory J. Matthews} 
\runningauthor{Whalen et al.}
\affil[1]{\protect\raggedright 
Loyola University Chicago, Department of Mathematics and Statistics, Chicago, IL, USA, e-mail: mwhalen3@luc.edu}
\affil[2]{\protect\raggedright 
University of Texas at Austin, Department of Kinesiology and Health Education, Austin, TX, USA, e-mail: brian.mills@austin.utexas.edu}
\affil[3]{\protect\raggedright 
Loyola University Chicago, Department of Mathematics and Statistics, Chicago, IL, USA, e-mail: gmatthews1@luc.edu}

@@

\begin{Schunk}
\begin{Soutput}
[1] "g"          "r"          "ab"         "sb"         "hr"        
[6] "bb"         "so"         "attendance"
\end{Soutput}
\begin{Soutput}
   year_id  franch_id          g          r         ab         sb         hr 
         0          0          0          0          0          0          0 
        bb         so attendance 
         0         16          0 
\end{Soutput}
\begin{Soutput}
 iter imp variable
  1   1  bb  so  sb  attendance
  1   2  bb  so  sb  attendance
  1   3  bb  so  sb  attendance
  1   4  bb  so  sb  attendance
  1   5  bb  so  sb  attendance
  2   1  bb  so  sb  attendance
  2   2  bb  so  sb  attendance
  2   3  bb  so  sb  attendance
  2   4  bb  so  sb  attendance
  2   5  bb  so  sb  attendance
  3   1  bb  so  sb  attendance
  3   2  bb  so  sb  attendance
  3   3  bb  so  sb  attendance
  3   4  bb  so  sb  attendance
  3   5  bb  so  sb  attendance
  4   1  bb  so  sb  attendance
  4   2  bb  so  sb  attendance
  4   3  bb  so  sb  attendance
  4   4  bb  so  sb  attendance
  4   5  bb  so  sb  attendance
  5   1  bb  so  sb  attendance
  5   2  bb  so  sb  attendance
  5   3  bb  so  sb  attendance
  5   4  bb  so  sb  attendance
  5   5  bb  so  sb  attendance
\end{Soutput}
\end{Schunk}
